The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-30 Writeup/paper_v3.tex
Address comments from Tim re: measurement error

>>>>

\rachel{Finally, we comment on whether the trends we
  have found could be caused by measurement noise rather than
  variations in the intrinsic shape distributions.  Measurement error
  tends to cause an increase in the RMS ellipticity due to the
  broadening of the measured ellipticity distributions.  However, this
is one of the reasons we restricted the sample to a magnitude of
23.5.  In this case, the $S/N$ of the flux measured in the galaxy
images is typically $\ge 50$.  If we consider the worst case, i.e.,
assume all galaxies have $S/N=50$ and use the Gaussian approximation
from \cite{BJ02}, the expected measurement error on the distortion is
$0.08$.  If we add this in quadrature with an RMS of $\sim 0.33$, then
the new RMS becomes $0.34$.  However, we see variations in the RMS
distortion in different environments that are as large as $0.05$, or
five times as large as this worst-case scenario due to measurement
noise.   Moreover, if measurement error were a significant issue, we
would expect it to affect the comparison of (for example) low- and
high-redshift samples in overdense regions.  In a volume-limited
sample, those will have different flux distributions and therefore
different SNR distributions.  However, there is little trend in the
RMS distortion with redshift for overdense regions, which suggests
empirically that measurement error is not a significant factor in our results.}
